---
title: "R Movies"
output: html_notebook
---

## Data Source

> The data source is located [here](https://www.kaggle.com/beyjin/movies-1990-to-2017/home).

### Packages
```{r packages, results='hide'}
library(dplyr)
library(stringr)
library(ggplot2)
```

### Overview

This is an analisis about the movies dataset

### Download

The data needs to be downloaded and unzipped.

```{r, echo=T}
url <- "https://www.kaggle.com/beyjin/movies-1990-to-2017/downloads/"
data_folder <- "data"
archive_type <- ".zip"

dataset <- "movies-1990-to-2017"
dataset_zip <- paste0("movies-1990-to-2017", archive_type)

# Download the data
if (!file.exists(file.path(data_folder, dataset_zip))) {
  download.file(paste0(url, dataset), file.path(data_folder, dataset_zip))
}

# unzip data
unzip(file.path(data_folder, dataset_zip), exdir = data_folder, overwrite = F)

# Display the unzipped files
list.files('data/', recursive=T)
```
## Loading the dataset

```{r, echo=T}
dataset_files <- c("Movie_Actors", "Movie_AdditionalRating", "Movie_Genres", "Movie_Movies", "Movie_Writer")
suffix <- ".csv"

for (f in dataset_files) {
  path <- file.path(data_folder, paste0(f, suffix))
  assign(f, read.csv(path))
  print(paste(f, "object size is", format(object.size(get(f)),units="Mb")))
}
```

## Movie analisis

We are going to analize some interesting data from movies.

### Cleaning N/A data

```{r}
# Check NA's
na_movies <- Movie_Movies %>%
  filter(is.na(Year))

knitr::kable(head(na_movies, 10))
```

```{r}
# Check NA's
na_movies <- Movie_Movies %>%
  filter(is.na(Year))

knitr::kable(head(na_movies, 10))
```

### Converting to integers year data

```{r warning=T}
# Check NA's
integer_movies_per_year <- Movie_Movies %>%
  #if_else()
  select(Year)
  #str_length(Year)
  #mutate(Year = if_else(str_length(Year) > 4, as.integer(str_split(Year, "-", simplify = T)[1]), as.integer(Year)))
  #stri_length(Year)
  #mutate(Year = as.integer(Year))
```

### Number of movies produced by top 10 director's?

The first question that may be asked is how many movies were produced by the top 10 directors.
```{r}
# Number of movies per year/decade
movies_per_director <- Movie_Movies %>%
  na.omit(movies_per_director) %>% # omit missing values
  select(imdbID, Director) %>% # select columns we need
  group_by(Director) %>% # group by director
  summarise(count = n())  %>% # count movies per director
  arrange(desc(count))

knitr::kable(head(movies_per_director, 10))
```

### How many movies were produced per year?

The first question that may be asked is how many movies were produced year by year. We can easily extract this information from the `movies_df` data frame.
```{r}
# Number of movies per year/decade
movies_per_year <- Movie_Movies %>%
  na.omit() %>% # omit missing values
  select(imdbID, Year) %>% # select columns we need
  group_by(Year) %>% # group by year
  summarise(count = n())  %>% # count movies per year
  arrange(Year)

knitr::kable(head(movies_per_year, 20))
```


 That's better. Now let's plot what we have.
```{r q1-2}
movies_per_year %>%
  ggplot(aes(x = count, y = Year)) +
  geom_line(color="blue") + 
  scale_x_continuous(limits = c(0, 10))
```